Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-07-30 Multiresolution_framework/ltx/response_to_reviews.tex

			\end{enumerate}  
			\subsection{Moderate concerns} 
			\begin{enumerate} 
			 \item Page 2: the authors should clearly define the difference between neural field and neural mass models.

			\emph{\parham{We have added the following paragraph on page 2: The main difference between these two classes is that neural field models describe the spatiotemporal evolution of a particular variable such as firing rate, membrane voltage or synaptic activity defined as the statistical expectation taken over a neural population while neural mass models describe such a quantity over time only, assuming that neurons are localized at approximately the same spatial location.}}

			\item Eqn 3: theta needs indexing

			\emph{\parham{Authors think that the reviewer is after Eqn 2. for the correction.  We have rewritten Eqn 2 by removing the parameter $\theta$ in order to be consistent with the rest of equation and we have described the coupling strength or synaptic efficiency within the text under Eq 2.}}

@@

			\item Define first and second order synaptic responses (used in figure 2 to explain text that does not refer to these terms)

			\emph{\parham{Definitions of first and second order synaptic responses have been added to the text under Eq.2.}}

### 2012-07-30 Multiresolution_framework/ltx/manuscript.tex
minor edit
4.2.2

Typically, the experimentalist only has access to the net field generated by the multi-resolution architecture of the cortex. Following this, it is natural to ask how do we best describe the multi-resolution structure of the neural system. The solution to this problem was proposed by \citet{Breakspear2005} in using a wavelet decomposition. This paper is directed at developing a framework for patient-specific multi-resolution neural field models, forming a fundamental link between data and theory. 
\section{IDE Neural Field Model}
In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
\begin{equation}
	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
	\int_{-\infty}^t 
	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
	\theta\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
	\underbrace{f\left( v\left( \mathbf{r}',t'\right)\right)}_{\text{firing}}
	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$. The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate. The parameter $\theta$ can be thought of as the synaptic efficiency or coupling strength, where $\theta>0$ and $\theta<0$ describe excitation and inhibition, respectively. There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, \parham{leading to first and second order differential equations}. These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line). The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features}. Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms. These are also shown in Fig.~\ref{fig:Modelcomponents}. The form of $w(\mathbf{r},\mathbf{r}')$ typically describes a Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}. By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel. In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.

>>>>

Typically, the experimentalist only has access to the net field generated by the multi-resolution architecture of the cortex. Following this, it is natural to ask how do we best describe the multi-resolution structure of the neural system. The solution to this problem was proposed by \citet{Breakspear2005} in using a wavelet decomposition. This paper is directed at developing a framework for patient-specific multi-resolution neural field models, forming a fundamental link between data and theory. 
\section{IDE Neural Field Model}
In a small network with no time delays the single layer homogeneous neural field model, in the most general form, is described by the equation
\begin{equation}
	\label{FullDoubleIntModel} \underbrace{v\left(\mathbf{r},t\right)}_{\text{field}} =
	\int_{-\infty}^t 
	\underbrace{h\left(t - t'\right)}_{\text{synapse}} \int_\Omega
	\underbrace{w\left(\mathbf{r},\mathbf{r}'\right)}_{\text{connectivity}} 
	\underbrace{f\left( v\left( \mathbf{r}',t'\right)\right)}_{\text{firing}}
	\, \mathrm{d}\mathbf{r}'\mathrm{d}t',
\end{equation}
where the post-synaptic membrane voltage at time $t$ of a population of neurons at position $\mathbf r$ within the spatial domain $\Omega$ is denoted by $v\left(\mathbf r,t\right)$. The function $h(t)$ describes the post-synaptic response kernel, $w\left(\mathbf{r},\mathbf{r}'\right)$ describes the connectivity kernel and $f(v(\mathbf{r},t))$ describes the relationship between the mean membrane potential and the mean firing rate. There are various forms of $h(t)$ that have been proposed in the literature, with different levels of complexity, \parham{leading to first and second order differential equations}. These are plotted in Fig.~\ref{fig:Modelcomponents}, \parham{showing finite rise time (solid line) versus instantaneous response (dotted line). The second order synaptic kernel reproduces  experimental excitatory and  inhibitory post-synaptic potentials (EPSP and IPSP) features \cite{VanRotterdam1982}}. Similarly, both the connectivity kernel and the activity function (firing rate) can take various forms. These are also shown in Fig.~\ref{fig:Modelcomponents}. The form of $w(\mathbf{r},\mathbf{r}')$ typically describes a Laplacian (exponential) or Gaussian decay in connectivity strength from any point in the field \cite{Breakspear2010,Atay2005}. By assuming the form of $h(t)$ is the same across layers (scales) the Amari style neural field model is formed, incorporating a multilayer structure into the connectivity kernel. \parham{The connectivity kernel then can be written as a sum of weighted Gaussian or Laplacian functions where the weights can be thought of as the synaptic efficiency or coupling strength where positive and negative weights describe excitation and inhibition, respectively.} In this way, the connectivity kernel typically takes the form of a Mexican hat (Gaussian shape within layer connectivity) or Wizard hat (Laplacian shape within layer) as depicted in Fig.~\ref{fig:Modelcomponents}.
